\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
grammar nits

The core of our analysis system is essentially an implementation of
Gough and Klaeren's static range analysis algorithm for bounds check
elimination.
We identify our technical contributions as:
\begin{itemize}
\item An implementation of Gough and Klaeren's range analysis in a
  modern industrial-strength SSA-based compiler.
\item A different algorithm for inserting and removing $\beta$ nodes
  that used by Gough and Klaeren that takes advantage of the data
  structures of a modern SSA compiler.
\item To facilitate the above, extended IonMonkey with a fast
  (constant time, one integer per basic block memory overhead) 
  mechanism for determining whether a block is dominated by another.
\item Extending the analysis to produce the information needed for
  overflow check elimination by differentiating between
  ``maximum/minimum 32-bit int values'' and ``infinity'' (possible
  overflow).
\item The observation that when doing range computation with the above
  distinction, the input ranges can be always be ``squashed'' to only
  finite ranges, since if overflow had occurred, the code would have
  bailed out.
\item An implementation of overflow check elimination using the above
  analyses.
\end{itemize}

@@

\section{IonMonkey Overview}
The IonMonkey compiler is somewhat loosely based on LLVM, in that it is an
imperative SSA compiler. IonMonkey takes the bytecode used by the SpiderMonkey
JavaScript interpreter and compiles it to native code. Optimistic type
specialization is used, and if type assumptions fail, then execution ``bails
out'' to the interpreter.

>>>>

The core of our analysis system is essentially an implementation of
Gough and Klaeren's static range analysis algorithm for bounds check
elimination.
We identify our technical contributions as:
\begin{itemize}
\item An implementation of Gough and Klaeren's range analysis in a
  modern industrial-strength SSA-based compiler.
\item A different algorithm for inserting and removing $\beta$ nodes
  that used by Gough and Klaeren that takes advantage of the data
  structures of a modern SSA compiler.
\item To facilitate the above, extending IonMonkey with a fast
  (constant time, one integer per basic block memory overhead) 
  mechanism for determining whether a block is dominated by another.
\item Extending the analysis to produce the information needed for
  overflow check elimination by differentiating between
  ``maximum/minimum 32-bit int values'' and ``infinity'' (possible
  overflow).
\item The observation that when doing range computation with the above
  distinction, the input ranges can be always be ``squashed'' to only
  finite ranges, since if overflow had occurred, the code would have
  bailed out.
\item An implementation of overflow check elimination using the above
  analyses.
\end{itemize}

@@

\section{IonMonkey Overview}
The IonMonkey compiler is somewhat loosely based on LLVM, in that it is an
imperative SSA-based compiler. IonMonkey takes the bytecode used by the SpiderMonkey
JavaScript interpreter and compiles it to native code. IonMonkey uses optimistic type
specialization, and if type assumptions fail, then execution ``bails
out'' to the interpreter. Bailout points are inserted when global effects take place.
